diffEnrich: An \proglang{R} Package to Compare Functional Enrichment Between Two Experimentally-derived Groups of Genes by Connecting to the KEGG REST API

### 2019-12-05 jss-article-rnw-diffEnrich/article.Rnw
V2 jss draft push

%% recommended packages
\usepackage{thumbpdf,lmodern}
\usepackage{textcomp}
\usepackage[section]{placeins}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{adjustbox}
\usepackage{makecell}
\usepackage{float}
\usepackage{longtable}
\newcommand\mc[1]{\multicolumn{1}{c}{#1}}

@@

%% For Sweave-based articles about R packages:
%% need no \usepackage{Sweave}
%% \SweaveOpts{engine=R, eps=FALSE, keep.source = TRUE}
<<preliminaries, echo=FALSE, results='hide'>>=
options(prompt = "R> ", continue = "+  ", width = 70, useFancyQuotes = FALSE)
library("MASS")
@

>>>>

%% recommended packages
\usepackage{thumbpdf,lmodern}
\usepackage{textcomp}
\usepackage[section]{placeins}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{adjustbox}
\usepackage{makecell}
\usepackage{float}
\usepackage{longtable}
\usepackage{listings}
\newcommand\mc[1]{\multicolumn{1}{c}{#1}}

@@

%% For Sweave-based articles about R packages:
%% need no \usepackage{Sweave}
%% \SweaveOpts{engine=R, eps=FALSE, keep.source = TRUE}
<<preliminaries, echo=FALSE, results='hide'>>=
options(prompt = "R> ", continue = "+  ", width = 70, useFancyQuotes = FALSE)

 options(width=70)

  listing <- function(x, options) {
    paste("\\begin{lstlisting}[basicstyle=\\ttfamily,breaklines=true]\n",
      x, "\\end{lstlisting}\n", sep = "")
  }
  knit_hooks$set(source=listing, output=listing)

@

### 2019-12-05 jss-article-rnw-diffEnrich/article.tex
V2 jss draft push

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{install.packages}\hlstd{(}\hlstr{"diffEnrich"}\hlstd{)}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcom{## Load package}
\hlkwd{suppressMessages}\hlstd{(}\hlkwd{library}\hlstd{(diffEnrich))}
\hlcom{## run get_kegg() using rat}
\hlstd{kegg_rno} \hlkwb{<-} \hlkwd{get_kegg}\hlstd{(}\hlstr{'rno'}\hlstd{)}
\end{alltt}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcom{## run get_kegg() using rat}
\hlstd{kegg_rno} \hlkwb{<-} \hlkwd{get_kegg}\hlstd{(}\hlstr{'rno'}\hlstd{)}
\end{alltt}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcom{## run get_kegg() using rat}
\hlstd{date} \hlkwb{<-} \hlkwd{as.character}\hlstd{(}\hlkwd{Sys.Date}\hlstd{())}
\hlstd{kegg_rno} \hlkwb{<-} \hlkwd{get_kegg}\hlstd{(}\hlkwc{read} \hlstd{=} \hlnum{TRUE}\hlstd{,}
                     \hlkwc{path} \hlstd{= here}\hlopt{::}\hlkwd{here}\hlstd{(),}
                     \hlkwc{date} \hlstd{= date,}
                     \hlkwc{release} \hlstd{=} \hlstr{"92"}\hlstd{)}
\end{alltt}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcom{## View sample gene lists from package data}
\hlkwd{head}\hlstd{(geneLists}\hlopt{$}\hlstd{list1)}
\end{alltt}
\begin{verbatim}
## [1] "361692"    "293654"    "293655"    "500974"    "100361529"
## [6] "171434"
\end{verbatim}
\begin{alltt}
\hlkwd{head}\hlstd{(geneLists}\hlopt{$}\hlstd{list2)}
\end{alltt}
\begin{verbatim}
## [1] "315547" "315548" "315549" "315550" "50938"  "58856"
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{head}\hlstd{(list1_pe}\hlopt{$}\hlstd{enrich_table)}
\end{alltt}
\begin{verbatim}
##     KEGG_PATHWAY_ID
## 95         rno04530
## 172        rno05135
## 194        rno05210
## 212        rno05231
## 197        rno05213
## 66         rno04144
##                                   KEGG_PATHWAY_description
## 95                Tight junction - Rattus norvegicus (rat)
## 172           Yersinia infection - Rattus norvegicus (rat)
## 194            Colorectal cancer - Rattus norvegicus (rat)
## 212 Choline metabolism in cancer - Rattus norvegicus (rat)
## 197           Endometrial cancer - Rattus norvegicus (rat)
## 66                   Endocytosis - Rattus norvegicus (rat)
##     KEGG_PATHWAY_cnt KEGG_PATHWAY_in_list KEGG_DATABASE_cnt
## 95               170                   19              8856
## 172              128                   16              8856
## 194               88                   12              8856
## 212               99                   12              8856
## 197               58                    9              8856
## 66               275                   22              8856
##     KEG_DATABASE_in_list expected     enrich_p        p_adj
## 95                   295 5.662827 3.485551e-06 0.0005387284
## 172                  295 4.263776 4.919894e-06 0.0005387284
## 194                  295 2.931346 3.179635e-05 0.0023211334
## 212                  295 3.297764 1.032192e-04 0.0044701134
## 197                  295 1.932023 1.132216e-04 0.0044701134
## 66                   295 9.160456 1.224689e-04 0.0044701134
##     fold_enrichment
## 95         3.355214
## 172        3.752542
## 194        4.093683
## 212        3.638829
## 197        4.658328
## 66         2.401627
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{summary}\hlstd{(list1_pe)}
\end{alltt}
\begin{verbatim}
## 219 KEGG pathways were tested. 
##  Only KEGG pathways that contained at least 2 genes from gene_list were tested. 
##  KEGG pathway species: Rattus norvegicus (rat)
##  8856 genes from gene_list were in the KEGG data pull. 
##  p-value adjustment method: BH
##  36 pathways reached statistical significance after multiple testing correction at a cutoff of 0.05. 
##  
## Significant pathways: 
##  Tight junction
## Yersinia infection
## Colorectal cancer
## Choline metabolism in cancer
## Endometrial cancer
## Endocytosis
## Neurotrophin signaling pathway
## Thermogenesis
## Oocyte meiosis
## VEGF signaling pathway
## Thyroid hormone signaling pathway
## Hippo signaling pathway
## T cell receptor signaling pathway
## Apoptosis
## Hepatocellular carcinoma
## MAPK signaling pathway
## Focal adhesion
## Salmonella infection
## Non-alcoholic fatty liver disease (NAFLD)
## ErbB signaling pathway
## Sphingolipid signaling pathway
## Pancreatic cancer
## Progesterone-mediated oocyte maturation
## Alzheimer disease
## Endocrine resistance
## Adrenergic signaling in cardiomyocytes
## IL-17 signaling pathway
## Chronic myeloid leukemia
## Dopaminergic synapse
## Prostate cancer
## EGFR tyrosine kinase inhibitor resistance
## Hepatitis C
## Ras signaling pathway
## Acute myeloid leukemia
## Insulin signaling pathway
## Fc epsilon RI signaling pathway
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcom{## Perform differential enrichment}
\hlstd{diff_enrich} \hlkwb{<-} \hlkwd{diffEnrich}\hlstd{(}\hlkwc{list1_pe} \hlstd{= list1_pe,}
                          \hlkwc{list2_pe} \hlstd{= list2_pe,}
                          \hlkwc{method} \hlstd{=} \hlstr{'none'}\hlstd{,}
                          \hlkwc{cutoff} \hlstd{=} \hlnum{0.05}\hlstd{)}
\end{alltt}
\end{kframe}
\end{knitrout}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{head}\hlstd{(diff_enrich}\hlopt{$}\hlstd{de_table)}
\end{alltt}
\begin{verbatim}
##          KEGG_PATHWAY_ID
## rno04530        rno04530
## rno05135        rno05135
## rno05210        rno05210
## rno05213        rno05213
## rno04660        rno04660
## rno04657        rno04657
##                                             KEGG_PATHWAY_description
## rno04530                    Tight junction - Rattus norvegicus (rat)
## rno05135                Yersinia infection - Rattus norvegicus (rat)
## rno05210                 Colorectal cancer - Rattus norvegicus (rat)
## rno05213                Endometrial cancer - Rattus norvegicus (rat)
## rno04660 T cell receptor signaling pathway - Rattus norvegicus (rat)
## rno04657           IL-17 signaling pathway - Rattus norvegicus (rat)
##          KEGG_PATHWAY_cnt KEGG_DATABASE_cnt KEGG_PATHWAY_in_list1
## rno04530              170              8856                    19
## rno05135              128              8856                    16
## rno05210               88              8856                    12
## rno05213               58              8856                     9
## rno04660              106              8856                    11
## rno04657               95              8856                     9
##          KEGG_DATABASE_in_list1 expected_list1 enrich_p_list1
## rno04530                    295       5.662827   3.485551e-06
## rno05135                    295       4.263776   4.919894e-06
## rno05210                    295       2.931346   3.179635e-05
## rno05213                    295       1.932023   1.132216e-04
## rno04660                    295       3.530939   7.743416e-04
## rno04657                    295       3.164521   4.270915e-03
##           p_adj_list1 fold_enrichment_list1 KEGG_PATHWAY_in_list2
## rno04530 0.0005387284              3.355214                   131
## rno05135 0.0005387284              3.752542                   105
## rno05210 0.0023211334              4.093683                    81
## rno05213 0.0044701134              4.658328                    55
## rno04660 0.0129121321              3.115318                    79
## rno04657 0.0346418644              2.844032                    59
##          KEGG_DATABASE_in_list2 expected_list2 enrich_p_list2
## rno04530                   5308      101.89250   1.459992e-06
## rno05135                   5308       76.71906   5.537739e-08
## rno05210                   5308       52.74435   9.806872e-12
## rno05213                   5308       34.76332   1.160182e-09
## rno04660                   5308       63.53297   1.107477e-03
## rno04657                   5308       56.93993   3.737223e-01
##           p_adj_list2 fold_enrichment_list2 odd_ratio diff_enrich_p
## rno04530 5.568342e-06              1.285669 0.3676651  0.0002935876
## rno05135 2.594826e-07              1.368630 0.3520039  0.0005434729
## rno05210 1.237175e-10              1.535709 0.3655602  0.0032572306
## rno05213 8.849757e-09              1.582127 0.3328275  0.0058774642
## rno04660 2.256227e-03              1.243449 0.3901694  0.0072047984
## rno04657 4.591045e-01              1.036180 0.3572935  0.0087537607
##          diff_enrich_adjusted
## rno04530         0.0002935876
## rno05135         0.0005434729
## rno05210         0.0032572306
## rno05213         0.0058774642
## rno04660         0.0072047984
## rno04657         0.0087537607
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{summary}\hlstd{(diff_enrich)}
\end{alltt}
\begin{verbatim}
## 219 KEGG pathways were shared between gene lists and were tested. 
##  KEGG pathway species: Rattus norvegicus (rat)
##  8856 genes from gene_list were in the KEGG data pull. 
##  p-value adjustment method: none
##  19 pathways reached statistical significance after multiple testing correction at a cutoff of 0.05. 
##  
## Significant pathways: 
##  Tight junction
## Yersinia infection
## Colorectal cancer
## Endometrial cancer
## T cell receptor signaling pathway
## IL-17 signaling pathway
## Salmonella infection
## Choline metabolism in cancer
## Endocytosis
## VEGF signaling pathway
## Oocyte meiosis
## Thermogenesis
## Hippo signaling pathway
## Neurotrophin signaling pathway
## Apoptosis
## Hepatocellular carcinoma
## Fc epsilon RI signaling pathway
## Thyroid hormone signaling pathway
## Alzheimer disease
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{figure}[H]
% \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcom{## Plot fold enrichment}
\hlkwd{plotFoldEnrichment}\hlstd{(}\hlkwc{de_res} \hlstd{= diff_enrich,} \hlkwc{pval} \hlstd{=} \hlnum{0.05}\hlstd{,} \hlkwc{N} \hlstd{=} \hlnum{5}\hlstd{)}
\end{alltt}
\end{kframe}
\includegraphics[width=5.0in,height=4in]{figure/visualization_2-1}

>>>>

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
install.packages("diffEnrich")\end{lstlisting}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
## Load package\end{lstlisting}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
suppressMessages(library(diffEnrich))\end{lstlisting}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
## run get_kegg() using rat\end{lstlisting}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
kegg_rno <- get_kegg('rno')\end{lstlisting}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
## run get_kegg() using rat\end{lstlisting}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
kegg_rno <- get_kegg('rno')\end{lstlisting}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
## run get_kegg() using rat\end{lstlisting}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
date <- as.character(Sys.Date())\end{lstlisting}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
kegg_rno <- get_kegg(read = TRUE,
                     path = here::here(),
                     date = date,
                     release = "92")\end{lstlisting}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
## View sample gene lists from package data\end{lstlisting}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
head(geneLists$list1)\end{lstlisting}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
## [1] "361692"    "293654"    "293655"    "500974"    "100361529"
## [6] "171434"
\end{lstlisting}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
head(geneLists$list2)\end{lstlisting}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
## [1] "315547" "315548" "315549" "315550" "50938"  "58856"
\end{lstlisting}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
head(list1_pe$enrich_table)\end{lstlisting}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
##     KEGG_PATHWAY_ID
## 95         rno04530
## 172        rno05135
## 194        rno05210
## 212        rno05231
## 197        rno05213
## 66         rno04144
##                                   KEGG_PATHWAY_description
## 95                Tight junction - Rattus norvegicus (rat)
## 172           Yersinia infection - Rattus norvegicus (rat)
## 194            Colorectal cancer - Rattus norvegicus (rat)
## 212 Choline metabolism in cancer - Rattus norvegicus (rat)
## 197           Endometrial cancer - Rattus norvegicus (rat)
## 66                   Endocytosis - Rattus norvegicus (rat)
##     KEGG_PATHWAY_cnt KEGG_PATHWAY_in_list KEGG_DATABASE_cnt
## 95               170                   19              8856
## 172              128                   16              8856
## 194               88                   12              8856
## 212               99                   12              8856
## 197               58                    9              8856
## 66               275                   22              8856
##     KEG_DATABASE_in_list expected     enrich_p        p_adj
## 95                   295 5.662827 3.485551e-06 0.0005387284
## 172                  295 4.263776 4.919894e-06 0.0005387284
## 194                  295 2.931346 3.179635e-05 0.0023211334
## 212                  295 3.297764 1.032192e-04 0.0044701134
## 197                  295 1.932023 1.132216e-04 0.0044701134
## 66                   295 9.160456 1.224689e-04 0.0044701134
##     fold_enrichment
## 95         3.355214
## 172        3.752542
## 194        4.093683
## 212        3.638829
## 197        4.658328
## 66         2.401627
\end{lstlisting}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
summary(list1_pe)\end{lstlisting}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
## 219 KEGG pathways were tested. 
##  Only KEGG pathways that contained at least 2 genes from gene_list were tested. 
##  KEGG pathway species: Rattus norvegicus (rat)
##  8856 genes from gene_list were in the KEGG data pull. 
##  p-value adjustment method: BH
##  36 pathways reached statistical significance after multiple testing correction at a cutoff of 0.05. 
##  
## Significant pathways: 
##  Tight junction
## Yersinia infection
## Colorectal cancer
## Choline metabolism in cancer
## Endometrial cancer
## Endocytosis
## Neurotrophin signaling pathway
## Thermogenesis
## Oocyte meiosis
## VEGF signaling pathway
## Thyroid hormone signaling pathway
## Hippo signaling pathway
## T cell receptor signaling pathway
## Apoptosis
## Hepatocellular carcinoma
## MAPK signaling pathway
## Focal adhesion
## Salmonella infection
## Non-alcoholic fatty liver disease (NAFLD)
## ErbB signaling pathway
## Sphingolipid signaling pathway
## Pancreatic cancer
## Progesterone-mediated oocyte maturation
## Alzheimer disease
## Endocrine resistance
## Adrenergic signaling in cardiomyocytes
## IL-17 signaling pathway
## Chronic myeloid leukemia
## Dopaminergic synapse
## Prostate cancer
## EGFR tyrosine kinase inhibitor resistance
## Hepatitis C
## Ras signaling pathway
## Acute myeloid leukemia
## Insulin signaling pathway
## Fc epsilon RI signaling pathway
\end{lstlisting}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
## Perform differential enrichment\end{lstlisting}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
diff_enrich <- diffEnrich(list1_pe = list1_pe,
                          list2_pe = list2_pe,
                          method = 'none',
                          cutoff = 0.05)\end{lstlisting}
\end{kframe}
\end{knitrout}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
head(diff_enrich$de_table)\end{lstlisting}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
##          KEGG_PATHWAY_ID
## rno04530        rno04530
## rno05135        rno05135
## rno05210        rno05210
## rno05213        rno05213
## rno04660        rno04660
## rno04657        rno04657
##                                             KEGG_PATHWAY_description
## rno04530                    Tight junction - Rattus norvegicus (rat)
## rno05135                Yersinia infection - Rattus norvegicus (rat)
## rno05210                 Colorectal cancer - Rattus norvegicus (rat)
## rno05213                Endometrial cancer - Rattus norvegicus (rat)
## rno04660 T cell receptor signaling pathway - Rattus norvegicus (rat)
## rno04657           IL-17 signaling pathway - Rattus norvegicus (rat)
##          KEGG_PATHWAY_cnt KEGG_DATABASE_cnt KEGG_PATHWAY_in_list1
## rno04530              170              8856                    19
## rno05135              128              8856                    16
## rno05210               88              8856                    12
## rno05213               58              8856                     9
## rno04660              106              8856                    11
## rno04657               95              8856                     9
##          KEGG_DATABASE_in_list1 expected_list1 enrich_p_list1
## rno04530                    295       5.662827   3.485551e-06
## rno05135                    295       4.263776   4.919894e-06
## rno05210                    295       2.931346   3.179635e-05
## rno05213                    295       1.932023   1.132216e-04
## rno04660                    295       3.530939   7.743416e-04
## rno04657                    295       3.164521   4.270915e-03
##           p_adj_list1 fold_enrichment_list1 KEGG_PATHWAY_in_list2
## rno04530 0.0005387284              3.355214                   131
## rno05135 0.0005387284              3.752542                   105
## rno05210 0.0023211334              4.093683                    81
## rno05213 0.0044701134              4.658328                    55
## rno04660 0.0129121321              3.115318                    79
## rno04657 0.0346418644              2.844032                    59
##          KEGG_DATABASE_in_list2 expected_list2 enrich_p_list2
## rno04530                   5308      101.89250   1.459992e-06
## rno05135                   5308       76.71906   5.537739e-08
## rno05210                   5308       52.74435   9.806872e-12
## rno05213                   5308       34.76332   1.160182e-09
## rno04660                   5308       63.53297   1.107477e-03
## rno04657                   5308       56.93993   3.737223e-01
##           p_adj_list2 fold_enrichment_list2 odd_ratio diff_enrich_p
## rno04530 5.568342e-06              1.285669 0.3676651  0.0002935876
## rno05135 2.594826e-07              1.368630 0.3520039  0.0005434729
## rno05210 1.237175e-10              1.535709 0.3655602  0.0032572306
## rno05213 8.849757e-09              1.582127 0.3328275  0.0058774642
## rno04660 2.256227e-03              1.243449 0.3901694  0.0072047984
## rno04657 4.591045e-01              1.036180 0.3572935  0.0087537607
##          diff_enrich_adjusted
## rno04530         0.0002935876
## rno05135         0.0005434729
## rno05210         0.0032572306
## rno05213         0.0058774642
## rno04660         0.0072047984
## rno04657         0.0087537607
\end{lstlisting}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
summary(diff_enrich)\end{lstlisting}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
## 219 KEGG pathways were shared between gene lists and were tested. 
##  KEGG pathway species: Rattus norvegicus (rat)
##  8856 genes from gene_list were in the KEGG data pull. 
##  p-value adjustment method: none
##  19 pathways reached statistical significance after multiple testing correction at a cutoff of 0.05. 
##  
## Significant pathways: 
##  Tight junction
## Yersinia infection
## Colorectal cancer
## Endometrial cancer
## T cell receptor signaling pathway
## IL-17 signaling pathway
## Salmonella infection
## Choline metabolism in cancer
## Endocytosis
## VEGF signaling pathway
## Oocyte meiosis
## Thermogenesis
## Hippo signaling pathway
## Neurotrophin signaling pathway
## Apoptosis
## Hepatocellular carcinoma
## Fc epsilon RI signaling pathway
## Thyroid hormone signaling pathway
## Alzheimer disease
\end{lstlisting}
\end{kframe}
\end{knitrout}

@@

\begin{figure}[H]
% \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
## Plot fold enrichment\end{lstlisting}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
plotFoldEnrichment(de_res = diff_enrich, pval = 0.05, N = 5)\end{lstlisting}
\end{kframe}
\includegraphics[width=5.0in,height=4in]{figure/visualization_2-1}
